Julia for HPC: In Situ Data Analysis with Julia for Climate Simulations at Large Scale

### 2024-04-15 paper/paper.tex
Update paper.tex

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{paper/figures/analysisoverhead.pdf}
    \caption{In situ data analysis overhead (ratios of in situ data analysis time to the total EAM time).}
    \label{fig:ssw_break}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{paper/figures/infrastructureoverhead.pdf}
    \caption{In situ infrastructure overhead (ratios of in situ infrastructure overhead time to the total EAM time).}
    \label{fig:pca_break}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{figures/analysisoverhead.pdf}
    \caption{In situ data analysis overhead (ratios of in situ data analysis time to the total EAM time).}
    \label{fig:ssw_break}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{figures/infrastructureoverhead.pdf}
    \caption{In situ infrastructure overhead (ratios of in situ infrastructure overhead time to the total EAM time).}
    \label{fig:pca_break}
\end{figure}
